### 2017-01-11 paper/evaluation.tex
pass on RQ2

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost from a regression-test is distributed
among the test cases?}
\newcommand{\RQC}{How often parallelization settings appear in
build files?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQE}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

@@

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjsTotal{} projects we analyzed.  A key factor to determine if
low-level parallelism will be effective to speedup test execution is
to identify whether or not a small fraction of tests dominate test
suite execution time.  If that is the case, it is unlikely that test
suite parallelization will help as a test artifact is the smallest
working unit in test frameworks (see Section~\ref{sec:frameworks}).
Ideally, one would hope that time is distributed uniformly across
tests in the suite.

@@

To evaluate the distribution of time, we analyzed the execution time
for the \numMedLong{} projects from the \longg{} and \medg{} groups
(see Section~\ref{sec:rqA}).

For each subject we calculated the
relative standard deviation of the test cases: we collected the
elapsed time of each individual test, calculated the standard
deviation, and divided by the mean. \Jbc{I need to clarify the
  relationship "well/bad-balanced" regression test and relative
  standard deviation}

Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
different groups of subjects}\Fix{TODO: collect data + compute the
statistic, create a scatter plot to identify groups of subjects}

\Jbc{I shouldn't introduce parallelization arguments here but we have
to address this at some point:
Regression tests that are well distributed may benefit from
parallelism since more tests executes at the same time while the
opposite scenario may require a different approach. In the later
scenario, executing tests in parallel may have insignificant impact
since a small subset of test cases dominates the execution.}

>>>>

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  regression test suites in open-source projects?}
\newcommand{\RQB}{How time is distributed across test cases?}
\newcommand{\RQC}{How often parallelization settings appear in build
  files?}  \newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQE}{What factors contribute to improve performance
  through parallelization?\Jbc{Previously as "When does
    parallelization works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

@@

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjsTotal{} projects we analyzed.  However, use of parallelism
does not assure speedups on those projects.  We analyzed one sensible
factor that is critical to the effectiveness of parallelism: the
amount of tests that dominate execution time.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

@@

We evaluated the dispersion of time distributions (one distribution
per project) to aswer research question RQ2.  To measure dispersion
\emph{across} projects we used Relative Standard Deviation
(RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were to
analyze each project in isolation, the standard deviation of a
distribution ($\sigma$) would suffice to quantify how dispersed the
(time) distribution is.  However, in our case, we would like to be
able to compare and summarize dispersion across projects.  The RSD,
which is obtained dividing the standard deviation by the mean ($\mu$)
of a distribution, provides such normalization effect.  This metric
provides a lower bound (zero) but not an upper bound (somewhere close
to 1).  The smaller (larger) the value of RSD the more (less) uniform
the distribution is.  Consequently, ignoring other factors that affect
performance of parallelization (e.g., CPU/IO ratio), the lower the
value of RSD the more parallelizable a test suite should be.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{R/relativeSD.pdf}  
  \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
    across projects.\Fix{update (mocked) data}}
\end{figure}

Figure~\ref{fig:relativesd} shows the distribution of RSD across
medium and long-running projects.  Results show that the distribution
is skewed to the right indicating that test costs are relatively well
distributed in most costly projects we analyzed \Fix{$\leftarrow$
  confirm}.

%% analyzed the execution time
%% for the \numMedLong{} projects from the \longg{} and \medg{} groups
%% (see Section~\ref{sec:rqA}).
%% For each subject we calculated the
%% relative standard deviation of the test cases: we collected the
%% elapsed time of each individual test, calculated the standard
%% deviation, and divided by the mean. \Jbc{I need to clarify the
%%   relationship "well/bad-balanced" regression test and relative
%%   standard deviation}

%% Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
%% different groups of subjects}\Fix{TODO: collect data + compute the
%% statistic, create a scatter plot to identify groups of subjects}

%% \Jbc{I shouldn't introduce parallelization arguments here but we have
%% to address this at some point:
%% Regression tests that are well distributed may benefit from
%% parallelism since more tests executes at the same time while the
%% opposite scenario may require a different approach. In the later
%% scenario, executing tests in parallel may have insignificant impact
%% since a small subset of test cases dominates the execution.}
